Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-10-15 to_do_list.tex
Updated Ben's to do list

>>>>

Ben
\begin{itemize}
	\item R1: Finish \& Double Check Fearon reference [DONE]
		\item add appropriate language to memo if necessary [DONE]

	\item R1: Talk to Kristy about whether we want to offer a numerical example a la what R1 requests.

	\item R1: Tone down our claims about being novel and unique [DONE]

	\item R1: Double check that we have fixed the typo identified by R1 [DONE]

	\item R3: Read the literature referenced by R3 and add some cites [DONE]

	\item R3: Read Berg 2009 in particular and engage it at least briefly in the paper. [DONE]

\end{itemize}
